### 2023-06-09 resilience-safe-down.tex
sections
up

let us choose $\Bad$ as the set of states from which the counter $c_{mutex}$ is not bounded by $k$.
%			at least one counter is unbounded. 
This set is upward-closed by (upward) compatibility in VASS.

As an example, let us choose $\Safe=S-\Bad$ then since $\Bad=\uparrow \Bad$, we have: $\Safe=\downarrow \Safe$.
%
% \alain{definir  ideal-effective WSTS}
%
\begin{theorem}\label{up-down}
The resilience problem is decidable for ideal-effective WSTS with 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$
and
the additional hypothesis that
for all downward-closed set $D \subseteq S$, the set $\pred^*(D)$ is downward-closed.
% \alain{est-ce que  $\pred(D)$ is downward closed avec D downward closed serait suffisant ? si l'ordre est omega2 alors closbas+inclusion est wqo donc il faudrait juste que la suite croissante $pred^n(D)+le reste$ converge...}
\end{theorem}

@@

>>>>

Let us choose $\Bad$ as the set of states from which the counter $c_{mutex}$ is not bounded by $k$.
%			at least one counter is unbounded. 
This set is upward-closed by (upward) compatibility in VASS.

As an example, let us choose $\Safe=S \setminus \Bad$. Then, since $\Bad=\uparrow \Bad$, we have: $\Safe=\downarrow \Safe$.

%
% \alain{definir  ideal-effective WSTS}
%
\begin{theorem}\label{up-down}
The resilience problem is decidable for ideal-effective WSTS with 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$
and
the additional hypothesis that
for all downward-closed set $D \subseteq S$, the set $\pred^*(D)$ is downward-closed.
% \alain{est-ce que  $\pred(D)$ is downward closed avec D downward closed serait suffisant ? si l'ordre est omega2 alors closbas+inclusion est wqo donc il faudrait juste que la suite croissante $pred^n(D)+le reste$ converge...}
\end{theorem}

@@

\alain{indecidabilite en enlevant une ou des hypotheses: The resilience problem is undecidable for ideal-effective WSTS}

### 2023-06-09 resilience.tex
up

\mathieu{vérifier au passage que c'est vrai qu'il y a pas de résultats home-space WSTS}

@@

\begin{example}
Let us consider a $\mathds{Z}$-VASS with only one state $q$, one counter, and one transition that adds $+1$ to the counter, with $\Safe = \uparrow q(0)$, $\Bad = \downarrow q(-1)$,
then resilience hold (one always ends up in the positive integers) but not bounded resilience: for every bound $k$ there is an element of $\Bad$ e.g. $q(-k-1)$ which necessitate at least $k+1$ steps before it can reach $\Safe$. 
\end{example}

@@

In particular, the existing proofs of resilience use the decidability of reachability; but we wish to decide resilience for models with undecidable reachability.
%
\alain{il manque un résultat d'indecidabilité pour les 3 resilience pour les WSTS+...}
%	 and ideals are recursive 
Our result will rely on coverability instead of reachability. We moreover show undecidability when coverability is not decidable in the case $\Safe = \uparrow \Safe$.

\iffalse

\begin{proposition}\label{general}
\textcolor{red}{
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-bounded-resilient iff $\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Bad,\Safe)-resilient (CONJECTURE FOR NOW)
}
\end{proposition}

\begin{proof}
Resilient means that ...
\end{proof}

\fi

% \mathieu{En fait de plus en plus j'ai l'impression que on peut se passer des neutres: même dans une situation où on aurait des configurations neutre j'aurais tendance à dire qu'on peut se ramener à un cas safe complémentaire de bad en duplicants les neutres en deux parties, une avec "on a vu un very bad récement il faut aller vers safe" (et qui dans le nouveau modèle seraient donc bad) et une "on a pas vu de very bad tout vas bien" (et qui dans le nouveau modèle seraient donc safe)
% $=>$ Rédiger ça plus proprement}
While considering a sequence of configurations, every prefix is always 
either in the case that the latest visited $\Bad$ configuration has already been followed by a $\Safe$ configuration
or in the case that it still has to. 
Thus, in context, there are no true ``neutral'' configurations: either a neutral configuration is contextually ``$\Safe$'' because it follows a visit in a $\Safe$ configuration, either it is contextually ``$\Bad$'' because it follows a visit in a $\Bad$ configuration and has, accordingly, to reach a $\Safe$ one.
Hence we will consider not only $\Bad$ and $\Safe$ disjoint but
% w.l.o.g.
	also
$\Bad$ complement of $\Safe$,
in which case
if $\Bad$ is downward-closed then $\Safe$ is upward-closed and vice-versa.
Cases where $\Bad$ or $\Safe$ are not complements of each other, and share closure properties, i.e. are both downward-closed or both upward-closed,
have also been studied, 
see 
Appendix~\ref{case down down}
and
Appendix~\ref{case up up} for results.

>>>>

% \mathieu{vérifier au passage que c'est vrai qu'il y a pas de résultats home-space WSTS}

@@

\begin{example}
Let us consider a VASS with only one state $q$, one counter, and one transition that substracts $-1$ from the counter, with $\Safe = \downarrow q(0)$, $\Bad = \uparrow q(1)$,
then resilience hold (one always ends up in the positive integers) but not bounded resilience: for every bound $k$ there is an element of $\Bad$ e.g. $q(-k-1)$ which necessitate at least $k+1$ steps before it can reach $\Safe$. 
\end{example}

@@

In particular, the existing proofs of resilience use the decidability of reachability; but we wish to decide resilience for models with undecidable reachability.
%
%	 and ideals are recursive 
Our result will rely on coverability instead of reachability. We moreover show undecidability when coverability is not decidable in the case $\Safe = \uparrow \Safe$.

While considering a sequence of configurations, every prefix is always 
either in the case that the latest visited $\Bad$ configuration has already been followed by a $\Safe$ configuration
or in the case that it still has to. 
Thus, in context, there are no true ``neutral'' configurations: either a neutral configuration is contextually ``$\Safe$'' because it follows a visit in a $\Safe$ configuration, either it is contextually ``$\Bad$'' because it follows a visit in a $\Bad$ configuration and has, accordingly, to reach a $\Safe$ one.
Hence we will consider not only $\Bad$ and $\Safe$ disjoint but
% w.l.o.g.
	also
$\Bad$ complement of $\Safe$,
in which case
if $\Bad$ is downward-closed then $\Safe$ is upward-closed and vice-versa.
Cases where $\Bad$ or $\Safe$ are not complements of each other, and share closure properties, i.e. are both downward-closed or both upward-closed,
have also been studied, 
see 
Appendix~\ref{case down down}
and
Appendix~\ref{case up up} for results.
